\documentclass[11pt]{article}

\title{\textbf{Wikipedia through Time}}
\date{}

\begin{document}

\maketitle

\section{The Main Story}
The English vocabulary has changed over time. Can we use that change in vocabulary to estimate the change in our ideas on Wikipedia? What would wikipedia have looked like in 1800?

\section{The Words}
First we have a time series of the number of words.

\section{Creating Wikipedia}
Then we use that to create a historical wikipedia in every year. If the title of a wikipedia article has a word that has not in the dictionary, we don't include that article.\\\\
How many words are in wikipedia article names that are not in the word database? Are these a problem? \\
\indent We have 1.5 million articles in 2000. Wikipedia has 5 million articles. That is 30\% of wikipedia. Most of these are proper nouns.\\\\
What about function words?\\
\indent They are included in the dictionary.

\section{Time Series of Articles and Words}
Now let's examine the time series of the number of articles and the number of words?\\
Can we create a linear transformation between the two graphs?\\
What puts these two concepts together?
    
\section{What does the graph look like?}
Now let's compare how connected this graph is compared to the original wikipedia?\\
Measure using degree distribution and invalid links.

\section{Visits}
Now let's examine how the most visited article changes over time?\\
What is the anchor or influential theme or notion in the articles?

\section{Funnels}
Now let's examine how the largest funnel changes over time?\\
What is the anchor or influential theme or notion in the articles?

\section{Other}

What's the frequency of words from each decade used in article titles today?
\\\\
Look at diff of each decade of new words and new articles that are added.


\end{document}
